---
title: "Gender Research Proposal"
author: "Arianna Zavala"
date: '2023-01-09'
output:
  pdf_document: default
  html_document: default
---


# Proposal Script


### STEP1: Bringing data
```{r}
library(rio)
lkData = "https://github.com/AriannaNKZC/UniMaGenderStudies/blob/main/data_gender_studies_fin.xlsx?raw=true"
data=import(lkData)
data$`Same Sex Marriage`
```


### STEP2: Exploring how is data distribution by making a graphic

```{r}
library(ggplot2)
ggplot(data, aes(x = Year, fill = factor(`Same Sex Marriage`))) +
        ylab("Number of Latin-American Countries") +
        geom_bar(stat = "count") +
        scale_fill_discrete(name = "Acceptance of Same Sex Marriage",
                       labels = c("no", "yes"))
```

This indicates that there has been an increase in Latin American countries recognizing same-sex marriage in the last 12 years.


#### Lets change one name variable to make it easier to work witk

```{r}
names(data)[3] = "sexmarriage"
names(data)[6] = "USA"
```


### STEP 2: Logistic regresion
Binominal variable

#### Hypothesis one

H1. The odds of a Latin-America country legalizing same-sex marriage increase when critical countries have a high index of LGBT legislation. 

#### Consideration of critical countries

```{r}
set.seed(2019)
#first model  - considering just Spain
rlog1 <- glm(sexmarriage ~ Spain, data = data, family = 'binomial')

#second model - considering just Portugal
rlog2 <- glm(sexmarriage ~ Portugal, data = data, family = 'binomial')

#third model - considering just France
rlog3 <- glm(sexmarriage ~ France, data = data, family = 'binomial')

#fourth model - considering just Germany
rlog4 <- glm(sexmarriage ~ Germany, data = data, family = 'binomial')

#fifht model = considering just USA
rlog5 <- glm(sexmarriage ~ USA, data = data, family = 'binomial')

#sixth model = considering just China
rlog6 <- glm(sexmarriage ~ China, data = data, family = 'binomial')

#seventh model = considering just Brazil
rlog7 <- glm(sexmarriage ~ Brazil, data = data, family = 'binomial')

#eight model = considering just Argentina
rlog8 <- glm(sexmarriage ~ Argentina, data = data, family = 'binomial')

#nine model - the aggrupation one

rlog9 <- glm(sexmarriage ~ Spain + Portugal + France + Germany + USA + China + Brazil + Argentina, data = data, family = 'binomial')

rlog91 <- glm(sexmarriage ~ Spain + Portugal + France + Germany + USA + Brazil + Argentina, data = data, family = 'binomial')

```


```{r}
#a nicer way to see the models
library(stargazer)
```

#### to see as group
```{r}
stargazer(rlog9, rlog91, type="text",report=("vc*p"))
```


#### to see individually 
```{r}
stargazer(rlog1,rlog2, rlog3, rlog4, rlog5, rlog6, rlog7, rlog8, type="text", report=("vc*p"))
```


#### hypothesis 2

H2. The odds of a Latin-America country legalizing same-sex marriage increased when Spain and Portugal had a high index of LGBT legislation.

#### Consideration of Spain and Portugal

```{r}
log1 <- glm(sexmarriage ~ Spain + Portugal, data = data, family = 'binomial')
stargazer(rlog1,rlog2, log1, type="text", report=("vc*p"))
```


#### hypothesis 3


H3. The odds of a Latin-America country legalizing same-sex marriage increased when the United States and China had a high index of LGBT legislation since they are superpowers.

#### hypothesis 4


H4. The odds of a Latin-America country legalizing same-sex marriage increased when the United States had a high index of LGBT legislation since they are superpowers.


#### Consideration of superpowers (China & US) and US

```{r}
log2 <- glm(sexmarriage ~ USA + China, data = data, family = 'binomial')
stargazer(rlog5,log2, type="text",report=("vc*p"))
```



#### hypothesis 5 

H5. The odds of a Latin-America country legalizing same-sex marriage increased when Argentina and Brazil had a high index of LGBT legislation since they are superpowers.

#### Consideration of Latinoamerican countries (Argentina and Brazil)

```{r}
log3 <- glm(sexmarriage ~ Brazil + Argentina, data = data, family = 'binomial')
stargazer(rlog7, rlog8, log3, type="text",report=("vc*p"))
```



```{r}
stargazer(rlog9, log1, rlog5,log2, log3, type="text",report=("vc*p"))
```

